% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{comment}

% Fonts
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[scaled=0.85]{beramono}

% Set your name here
\def\name{Joshua Branchaud}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  15819 Howard St. \\
  Omaha, NE 68118 \\
  (402) 660 1656
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Email: jbranchaud@gmail.com \\
  Website: joshbranchaud.com \\
  GitHub: @jbranchaud
\end{minipage}

% If this is for a specific job or type of job, include this objective
% section with a purpose or objective statement explaining what this resume
% is for. For example,
% "Seeking a position as a software engineer doing both front-end and
% back-end development"

%\section*{Objective}
%
%\begin{itemize}
%\end{itemize}

\section*{Education}

\begin{itemize}
  % Dec 18, 2010
  %\item High School Diploma, Millard North High School, Omaha NE, May 2007.

  % Include GPA with each education item?

  \item Bachelor of Science in Computer Science, University of Nebraska-Lincoln, May 2011.

    \begin{itemize}
        \item \textit{Minors:} Mathematics and Spanish
    \end{itemize}
    
    \item Master of Science in Computer Science, University of Nebraska-Lincoln, In
    progress.

\end{itemize}


\section*{Experience}

\begin{itemize}
\item \textbf{Full-time Volunteer, Young Adults in Global Mission of the ELCA}
\item \emph{Grand Bourg, Buenos Aires, Argentina, August 2013--July 2014}
	\begin{itemize}
    \item Accompanied the community of Congregation San Lucas, including
    administrative duties, youth and children's activities, and technology
    training and consulting.
    \item Facilitated skill-building workshops and taught computer skills at
    a vocational center for differently-abled adults.
    \item Partnered with a neighborhood school to provide after-school
    English language instruction.
	\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Graduate Research Assistant, UNL Department of Computer Science, advised by Dr. Anita Sarma}
\item \emph{Lincoln, Nebraska, August 2011--August 2013}
	\begin{itemize}
	\item Developed an Impact Analysis technique to be used for real-time
    workspace awareness.
    \item Coordinated research efforts among four
    geographically-distributed
    professional researchers, combining the areas of Program Analysis and
    Workspace Awareness.
    \item Published two research papers in top-tier software engineering
    conferences.
	\item Updated and refactored Palantir, a workspace awareness tool
    implemented in Java as an Eclipse plugin.
	\end{itemize}
\end{itemize}

% Commented Out This Experience Item
\begin{comment}
\begin{itemize}
\item \textbf{Host and Fellowship Coordinator, August 2012--July 2013}
\item \emph{Lutheran Student Center (ELCA), University of Nebraska-Lincoln}
    \begin{itemize}
    \item Clean and maintain the Lutheran Student Center building.
    \item Engage students with fun fellowship opportunities such as movie
    nights and pool leagues.
    \end{itemize}
\end{itemize}
\end{comment}

\begin{itemize}
\item \textbf{Student Intern, Formal Methods Group, NASA Langley, advised by Dr. Suzette Person}
\item \emph{Hampton, Virginia, May 2012--August 2012}
    \begin{itemize}
    \item Designed and implemented a framework that brings program analysis
    to a variety of client applications.
    \item Researched a strategy for efficiently analyzing heap allocated
    memory during symbolic execution of Java programs.
    \end{itemize}
\end{itemize}

% Commented Out This Experience Item
\begin{comment}
\begin{itemize}
\item \textbf{Teaching Assistant for CSE361 (Software Engineering), August 2011--December 2011}
\item \emph{University of Nebraska-Lincoln, Department of Computer Science}
	\begin{itemize}
    \item Developed a semester project, assisted in class, graded
    assignments.
	\end{itemize}
\end{itemize}
\end{comment}

\begin{itemize}
\item \textbf{Undergraduate Research Assistant, UNL Department of Computer Science, advised by Dr. Anita Sarma}
\item \emph{Lincoln, Nebraska, January 2010--August 2011}
	\begin{itemize}
    \item Maintained and updated Palantir, a workspace awareness tool
    implemented in Java as an Eclipse plugin.
    \item Researched topics related to my advisor's PhD area to prepare for
    gradute work.
	\end{itemize}
\end{itemize}

%\begin{itemize}
%\item Teaching Assistant for CSE155 (Introduction to CS), January 2010--May 2010
%\item \emph{University of Nebraska-Lincoln, Department of Computer Science}
%	\begin{itemize}
%	\item Assisted in lab sections, graded Java assignments, and held office hours
%	\end{itemize}
%\end{itemize}

%\begin{itemize}
%	\item Software Developer, NASA and Google Summer of Code, May 2011--August 2011
%	\begin{itemize}
%		\item Extended DiSE, a software verification tool, from intraprocedural to interprocedural
%		\item Developed Java examples for testing the tool
%		\item Work on this project is continuing into the Fall of 2011 outside of GSoC
%	\end{itemize}
%    \item Web Assistant, Kaul Design Group, August 2010--Present.
%	\begin{itemize}
%	\item Update Joomla!-based webpages
%	\item Modify HTML and CSS documents
%	\end{itemize}
%\end{itemize}

\section*{Skills}

\begin{itemize}
    \item Experience developing with Java, JavaScript, CSS, HTML, Ruby, Ruby on Rails,
    Objective-C (for iOS Development), Python, Bash scripts, Git, and
    Mercurial.
    \item Experience in Adobe Photoshop, Illustrator, and InDesign.
    \item Proficiency in Spanish.
\end{itemize}

\section*{Miscellaneous}

\begin{itemize}
    \item Open-source maintainer, captionss, splitting-atoms, etc., 2011--present.
    \item Co-founder and organizer, Lincoln's Beer and Code meetup, 2012--present.
    \item President, Beta Sigma Psi Fraternity, 2009--2011.
    \item Participant, ACM Regional Programming Competition, 2010.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
